\documentclass[aps,prd,preprint,superscriptaddress,nofootinbib]{revtex4-1}
\pdfoutput=1
\linespread{1}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage[svgnames]{xcolor}
\usepackage[caption=false]{subfig}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{listings} 
\usepackage[normalem]{ulem}
\usepackage{placeins}
%\usepackage{braket}
\usepackage{multirow}
\usepackage{tabulary}
\usepackage{hyperref}% add hypertext capabilities
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{soul}
%\usepackage{makecell}
\usepackage{siunitx}
\sisetup{separate-uncertainty=true}
\DeclareSIUnit\radlen{\text{\ensuremath{X_{\mathrm{0}}}}}
\DeclareSIUnit\clight{\text{\ensuremath{c}}} % remove 0 subscript from speed of light

\newcommand{\todo}[1]{{\color{red} (To Do: #1)}}
\newcommand{\blue}[1]{\textcolor{NALblue}{#1}}
\newcommand\addcite{[{\color{blue} \underline{CITATION NEEDED}}]}

\newcommand{\enu}{\ensuremath{E_{\nu}}\xspace}
\def\bracketbar{\hbox{\kern-9pt\raise1pt%
    \hbox{{\tiny(}{\lower1.5pt\hbox{\bf--}}{\tiny)}}}}

\begin{document}

\title{ProtoDUNE-ND: proposal to place the ArgonCube 2x2 Demonstrator module in a neutrino beamline at Fermilab}

\author{ArgonCube Collaboration}

\date{\today}

\begin{abstract}
  This document outlines the case for a neutrino beam test of the DUNE near detector (ND) at Fermilab, dubbed ProtoDUNE-ND. The proposed location for ProtoDUNE-ND is in the MINOS-ND hall, upstream of the current MINERvA/MINOS-ND locations, placing it on-axis in the NuMI medium energy neutrino beam. The core of ProtoDUNE-ND is the ArgonCube 2x2 Demonstrator module, a large scale demonstrator for the core liquid argon (LAr) component of the ND. A description of the ArgonCube 2x2 Demonstrator is given, together with a brief outline of the required infrastructure. Additionally, the possibility to include test modules for other DUNE ND component detectors is discussed. 
  An overview of the detector physics studies which can be completed with ProtoDUNE-ND is given, which will inform the final DUNE ND design choices, and aid in developing reconstruction tools in preparation for DUNE.
  Placing the 2x2 Demonstrator as a stand-alone underground in the NuMI beam will allow for the development and demonstration of the tools necessary to disentangle piled up events within the LAr.
  In the absence of DUNE ND demonstrators for the other technologies, existing detectors can be utilised.
  Pairing the 2x2 with MINERvA enables a test of the ability to track muons and fast neutrons from the slow and busy LAr detector into a fast-response detector, the keystone of the DUNE ND. 
  Additionally, by pairing the 2x2 with both MINERvA and MINOS the response of 2x2 can be characterised as a function of momentum, providing a validation of the momentum measurement via multiple coulomb scattering that will need to be used for side-exiting muons in both the DUNE ND and far detector.
  
\end{abstract}

\maketitle

% For now suppress the table of contents
%\tableofcontents

\input{introduction.tex}
\input{protodune-nd.tex}
\input{detector-physics-studies.tex}
\input{minerva.tex}
\input{outlook.tex}
\input{conclusions.tex}

%\begin{acknowledgments}
%Thanks for all the \$\$\$
%\end{acknowledgments}

\bibliography{bibliography.bib}% Produces the bibliography via BibTeX.

%\appendix
%\input{an_appendix}

\end{document}
