\section{Conclusions}
\label{sec:conclusions}

In this work, we have outlined the detector physics potential of the ProtoDUNE-ND testbench experiment in the MINOS-ND hall at Fermilab. At the heart of ProtoDUNE-ND sits the ArgonCube 2x2 demonstrator module, which is currently being commissioned, and will be moved to Fermilab by early 2020. The set-up of ProtoDUNE-ND is intended to be flexible, to allow for new modules testing different aspects of the future DUNE-ND design to be installed at different times. This is facilitated by the moveable cryogenic support systems which need to be tested for the DUNE-PRISM baseline design concept, and which will allow the ArgonCube 2x2 to be moved, and the ProtoDUNE-ND arrangement to be reconfigured as a result. The detector physics studies outlined in this document will provide vital inputs to the full-scale DUNE-ND design, and provide a much-needed intermediate scale test, scaling up the small R\&D tests which have already been carried out, and allowing for long-term stability tests to be carried out.

In this document, we have also outlined the detector physics case for incorporating elements of the soon to be decommissioned MINERvA detector into the ProtoDUNE-ND setup. All DUNE-ND designs considered in Ref.~\ref{dune_ndcsg} include some fast scintillator detector, but no prototype is foreseen at this time for ProtoDUNE-ND. MINERvA components would fill that gap, and provide an essential test of combined reconstruction across different detectors will very different readout technology and times. Additionally, we briefly discussed the possibility to include the MINOS-ND into ProtoDUNE-ND, which is due to be decommissioned along with the MINERA experiment in mid-2019. In combination, using elements of MINERvA and MINOS-ND in ProtoDUNE-ND would allow us to contain all particles in a large fraction of events, and provide a realistic test of the energy recontruction capabilities of the final DUNE-ND. This would be invaluable for DUNE-ND design studies, and would greatly enhance the impact of the ProtoDUNE-ND test.
