\section{Outlook and timeline}
\label{sec:outlook}
To provide some context for the aggressive schedule of the ArgonCube 2x2 Demonstrator and ProtoDUNE-ND: the Conceptual Design Report for the DUNE ND will be submitted in April of 2019, with the Technical Design Report to be submitted in April of the following year~\cite{dune_dates}, with installation due to begin in 2025. 

The 2x2 construction and commissioning will take place in Bern, before the detector is moved to Fermilab. To date, the various technologies have been demonstrated in small test stands, the next step is to test the module construction techniques. Once these tests are complete, the technologies can be scaled to populate a 2x2 module. The following is a very simplified timeline indicating the major milestones and contributing institutes:      

\begin{itemize}
\item {\bf December 2018:}
\begin{itemize}
\item Bern: Complete cryostat instrumentation and infrastructure: for cryogenic control systems and slow control monitoring. 
\item LBNL: LArPix V2 design to vendor. Packaging test with LArPix V1.
\end{itemize}
\item {\bf January 2019:} 
\begin{itemize}
	\item Bern: Test of first module, demonstrate purity can be maintained, confirm material choices, optimize cooling control and slow monitoring system.   
	\item LBNL: LArPix V2 review meeting. LArPix V2 Production.
	\item SLAC: Review resistive-shell TPC construction techniques. Review HV supply and distribution options.   
	\item FNAL: Control system development (PLC). Determine cryogenic infrastructure requirements at FNAL (ODH), and cost 
	estimate.  
\end{itemize}
\item {\bf February 2019:} FNAL: Cryogenic review meeting.  
\item {\bf March 2019:} Bern: Deploy FNAL PLC. Collaboration meeting, finalize module design and outline construction workload across collaboration.    
\item {\bf April 2019:} 
\begin{itemize}
	\item Rochester: Review rock-muon tagger. Finalize design concept of beam trigger and high level DAQ (event builder). 
	\item FNAL: Review MINOS ND hall installation concept.  
\end{itemize}
\item {\bf June 2019:} Collaboration: Preliminary MINOS ND hall installation plan.
\item {\bf July 2019:} 
\begin{itemize}
	\item LBNL: Testing of LArPix V2 on pixel PCB.   
	\item SLAC: Finalize TPC construction method.
	%\item Rochester: Review design options for movable 2x2 platform and sump.  
\end{itemize}
\item {\bf September/October 2019:} Collaboration work at Bern: module construction begins.
 \item {\bf November 2019:} Collaboration work at Bern: Module deployment.
\item {\bf December 2019:} 
\begin{itemize}
	\item Collaboration work at Bern: Cosmic run  2x2, DAQ tests and develop simple reconstruction tools.   
	\item FNAL: Review installation design.  
\end{itemize}
\item {\bf January 2020:}
\begin{itemize}
	\item Bern: Shipping to FNAL.
	\item Rochester at FNAL: Trigger/DAQ electronics installation and commissioning. 
\end{itemize}
\item {\bf February 2020:} Collaboration work at FNAL: 2x2 assembly and installation.
\item {\bf May 2020:} Collaboration work at FNAL: 2x2 commissioning.    
\item {\bf October 2020:} Collaboration work at FNAL: Beginning of beam data. Calibrations and data analysis.

\end{itemize}
