\documentclass[a4paper]{article}
%\documentclass[aps,prd,preprint,nofootinbib]{revtex4-1}
\pdfoutput=1
\linespread{1}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage[svgnames]{xcolor}
\usepackage[caption=false]{subfig}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{listings} 
\usepackage[normalem]{ulem}
\usepackage{placeins}
%\usepackage{braket}
\usepackage{multirow}
\usepackage{tabulary}
\usepackage{hyperref}% add hypertext capabilities
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{soul}
%\usepackage{makecell}

\usepackage[utf8]{inputenc} % utf8 support in source code
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage[autostyle]{csquotes} % recommended by biblatex
\usepackage{xpatch} % recommended by biblatex
\usepackage[backend=biber, giveninits, sorting=none, style=numeric-comp]{biblatex} % much more flexible than BibTeX
\addbibresource{bibliography.bib}

\usepackage{siunitx}
\sisetup{separate-uncertainty=true}

\newcommand{\todo}[1]{{\color{red} (To Do: #1)}}
\newcommand{\blue}[1]{\textcolor{NALblue}{#1}}
\newcommand\addcite{[{\color{blue} \underline{CITATION NEEDED}}]}

\newcommand{\enu}{\ensuremath{E_{\nu}}\xspace}
\def\bracketbar{\hbox{\kern-9pt\raise1pt%
    \hbox{{\tiny(}{\lower1.5pt\hbox{\bf--}}{\tiny)}}}}

\begin{document}


\begin{center}
		
	{\Large \bf DRAFT\\ 
		ProtoDUNE-ND-Tracker: extending the detector physics reach of ProtoDUNE-ND with existing detector components} 
	\vspace*{0.5cm}
	\setcounter{footnote}{0}  
	\def\A{\kern+.6ex\lower.42ex\hbox{$\scriptstyle \iota$}\kern-1.20ex a}
	\def\E{\kern+.5ex\lower.42ex\hbox{$\scriptstyle \iota$}\kern-1.10ex e}
	\small
	\newcommand{\Aname}[2]{#1}
	\def\titlefoot#1{\vspace{-0.3cm}\begin{center}{\bf #1}\end{center}}
	
	\Aname{J.~R.~Sinclair\footnote{Corresponding author: james.sinclair@lhep.unibe.ch}}{Bern} and
	\Aname{C.~Wilkinson\footnote{Corresponding author: callum.wilkinson@lhep.unibe.ch}}{Bern}
	\titlefoot{Albert Einstein Center for Fundamental Physics (AEC), Laboratory for High Energy Physics, University of Bern, 3012 Bern, Switzerland\label{Bern}}
	
	
\end{center}
\vspace*{1cm}

\begin{abstract}

In this document we propose introducing a tracking scintillator detector, ProtoDUNE-ND-Tracker, to extend the utility of the ProtoDUNE-ND proposal over the ArgonCube 2x2-only case, while no other DUNE ND subdetector prototypes are available. ProtoDUNE-ND-Tracker repurposes components of the existing MINERvA and MINOS-ND hardware already positioned on-axis in the NuMI beam, in the same detector hall as ProtoDUNE-ND is to be sited.

Using ProtoDUNE-ND-Tracker paired with the ArgonCube 2x2 Demonstrator, the response of the 2x2 can be characterized as a function of momentum, providing a validation of the momentum measurement via multiple coulomb scattering that will need to be used for side-exiting muons in both the DUNE ND and far detector. Pairing the 2x2 with MINERvA enables a test of the ability to track muons and fast neutrons from the slow and busy LAr detector into a fast-response detector, the keystone of the DUNE ND.

As ProtoDUNE-ND is designed to be easily reconfigurable, with a moveable cryogenic system for the ArgonCube 2x2 Demonstrator an important test of the DUNE-PRISM technical design, the ProtoDUNE-ND-Tracker would in no way preclude the introduction of future DUNE ND subdector prototypes, and is likely to prove invaluable for future reconfigurations of the design.
\todo{As of now, we have not design it to be moveable. If we pursue this, we need to change plans asap and find engineering support. Drop this last paragraph? Or, extend with a comment on the staged approach of DUNE-ND?}  

\end{abstract}



% For now suppress the table of contents
%\tableofcontents

\input{introduction.tex}
\input{minerva.tex}
\input{minos.tex}
\input{configuration.tex}
\input{costs.tex}
\input{conclusions.tex}

\printbibliography

%\begin{acknowledgments}
%Thanks for all the \$\$\$
%\end{acknowledgments}


%\bibliography{bibliography.bib}% Produces the bibliography via BibTeX.

%\appendix
%\input{an_appendix}

\end{document}
